Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
caption for figure 3 is revised

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bp]
	\plotonesc{radio_emission_ChristensenAubert_multiplecriteria.pdf}
   \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom). The systems are located at 100 pc away. The doubly hatched regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$. The hatched regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1 \nu_{\rm cyc}$, is below $\nu_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system. }
  \label{fig:radio}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bp]
	\plotonesc{radio_emission_ChristensenAubert_multiplecriteria.pdf}
   \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and that to an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom). The systems are located at 100 pc away. The doubly hatched regions show the parameter spaces where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$. The regions hatched with vertical lines show the parameter spaces where the frequencies of bulk radio emission is below $\nu_{\rm plasma}^{\rm los}$, i.e., $\nu_{\rm plasma}^{\rm los} > 0.1 \nu_{\rm cyc}$)}
  \label{fig:radio}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
